Experience Report: Kandria - A Game in Common Lisp

### 2023-04-03 els2023-kandria/paper.tex
Update

\documentclass[format=sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{float}
\usepackage[labelfont=bf,textfont=md]{caption}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage[all]{hypcap}
\usemintedstyle[common-lisp]{default}
\newmintinline[code]{text}{}
\bibliographystyle{plainnat}

@@

Kandria was funded in part by the Pro Helvetia Interactive Media Grant and the KPT Poland Prize Digital Dragons Accelerator.
\bibliography{paper}
\end{document}

>>>>

\documentclass[format=sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[showframe]{geometry}
\usepackage{enumitem}
\usepackage{float}
\usepackage[labelfont=bf,textfont=md]{caption}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage[all]{hypcap}
\usemintedstyle[common-lisp]{default}
\newmintinline[code]{text}{}
\bibliographystyle{plainnat}

@@

Kandria was funded in part by the Pro Helvetia Interactive Media Grant and the KPT Poland Prize Digital Dragons Accelerator.

\begin{figure*}
  \begin{centering}
    \includegraphics[width=1.0\textwidth]{flamegraph.png}
  \end{centering}
  \caption{A flamegraph of the game's main thread. Due to the high nesting not much is visible at this scale. We've identified two specific blocks belonging to collision resolution and rendering. The graph of a release build would look slightly different, as several things are optimised away for a release build.}
\end{figure*}

\bibliography{paper}

\end{document}
